Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-02-12 Ben_Manuscripts/thesis/transport.tex
starting dissertation

\documentclass[journal=jpcbfk,manuscript=article]{achemso}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
%\usepackage{array}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
%\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{multicol}
\usepackage{tcolorbox}

\SectionNumbersOn
%\definecolor{amber}{rgb}{1.0, 0.75, 0.0} % amber
%\definecolor{amber}{rgb}{1.0, 0.84, 0.0} % gold
\definecolor{amber}{rgb}{0.99, 0.76, 0.0} % golden poppy

\externaldocument[S-]{Supporting_Information}

\title{Chemically Selective Transport in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

\begin{document}

  \graphicspath{{./figures/}}

  \begin{abstract}

  The uniform size and complex chemical topology of the pores formed by
  self-assembled amphiphilic molecules such as liquid crystals make them
  promising candidates for selective separations.
  In this work, we observe transport of water, sodium ions and 20 small polar
  solutes within the pores of a lyotropic liquid crystal (LLC) membrane using
  atomistic molecular simulations. We find that the transport of a species is
  dependent not only on molecular size, but on chemical functionality as well.
  The membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. We observe that all
  solutes perform intermittent hops between lengthy periods of entrapment. Three
  different trapping mechanisms are responsible for this behavior. First, solutes
  that drift out of the pore can become entangled among the dense monomer tails.
  Second, solutes can donate hydrogen bonds to the monomer head groups. Third,
  solutes can coordinate with sodium counter ions.  The degree to which a solute
  is affected by each mechanism is dependent on the chemical functionality of the
  solute. Using the insights developed in this study, we can begin to think about
  how to redesign existing LLC membranes in order to perform solute-specific
  separations.

  \end{abstract}

@@

  Python scripts used to set up systems and conduct post-simulation trajectory 
  analysis (as described below and in the Supporting Information) are available 
  online at \\
  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. The 
  appropriate scripts to use for the subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information. We ran all 
  MD simulations and energy minimizations using GROMACS 2018.3.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}

  \subsection{Molecule Parameterization}\label{method:parameterization}

@@

  \section*{Supporting Information}

  Detailed explanations and expansions upon the results and procedures mentioned in
  the main text are described in the Supporting Information. This information is
  available free of charge via the Internet at http://pubs.acs.org.

  \section*{Acknowledgments}

  B.J.C. was supported by the Graduate Assistance in Areas of National Need (GAANN) 
  fellowship which is funded by the U.S. Department of Education.

  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation (NSF) grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the NSF (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.

  The authors thank Christopher Calderon and Gregory Morrin for helping kick start
  our studies of subdiffusive transport. Additionally, the authors thank 
  Douglas Gin and Richard Noble for their guidance on past and present experimental
  research on LLC membranes and for reading over this manuscript before submission.

  \clearpage

  \bibliographystyle{ieeetr}
  \bibliography{transport}

  \newpage

  \section*{TOC Graphic}

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=3.25in]{toc_transport.pdf}
  \end{figure}

\end{document}

% LocalWords:  lyotropic LLC solutes solute permeability micropollutants RO NF
% LocalWords:  groundwaters flowback nanofiltration bruggen Nanostructured feng
% LocalWords:  nanostructured mesophases Donnan Zhou al Dischinger BJC Hmm Na
% LocalWords:  selectivities physicochemical nanopores GA pKa's protonated pKa
% LocalWords:  gallic perrin pka NaGA MeOH URE EtOH acetamide AcN propanol PrOH
% LocalWords:  butanol BtOH mercaptoethanol EG sulfoxide DMSO PG dimercapto DMP
% LocalWords:  GLY tetrahydrofuran THF tetrose dimethylformamide DMF AcOH diols
% LocalWords:  triols MSD solute's readthedocs repo GROMACS gromacs der hess wt
% LocalWords:  Antechamber bccsym molcharge QUACPAC zhou Resel equil ca gmx COM
% LocalWords:  solvate solvated Parrinello barostat subdiffusive superdiffusive
% LocalWords:  subdiffusion CTRW MSDs ageing microfriction Gierer einstein Chan
% LocalWords:  MSD's comps li Rg appoximation polson bT fr CI Luzar Chandler py
% LocalWords:  hbonds VMD Roux genion disassociated Clauset martiniano Voloshin
% LocalWords:  timescales binned RDFs RDF tortuosity carboxylate pdf sodium's
% LocalWords:  mobilities timescale diffusivity msd tailvpore methanol's tamsds
% LocalWords:  msds sublinear ztraces COMs alkane COOH HOH hbond immobilization
% LocalWords:  counterions sulfinyl substituents electronegative COH coord na
% LocalWords:  Carvajal Wu Shinoda carboxy ATPase rdf counterintuitively Amides
% LocalWords:  unhindered propanol's butanol's hydrophilicity glycol's Ketones
% LocalWords:  hybridization amides electronegativity NH ketones Thiols SOH ACI
% LocalWords:  dimercaptoethanol dimethylsulfoxide rdfs mercaptoethanol's thiol
% LocalWords:  formamide nondonors nanoporous XSEDE PSC RMACC TET ribose EAC
% LocalWords:  berendsen spoel Rahman bulleted Wirtz TBD equilibrations thiols
% LocalWords:  hbonding DMS linkable permeabilities Calderon Morrin TOC

>>>>

\chapter{Chemically Selective Transport in the H\textsubscript{II} Phase}\label{chapter:transport}

  %\graphicspath{{./figs/}}
  %\graphicspath{{/home/bcoscia/PycharmProjects/LLC_Membranes/Ben_Manuscripts/transport/figures}}

@@

  Python scripts used to set up systems and conduct post-simulation trajectory 
  analysis (as described below and in the Supporting Information) are available 
  online at \\
  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. The 
  appropriate scripts to use for the subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts_transport} of the Supporting Information. We ran all 
  MD simulations and energy minimizations using GROMACS 2018.3.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}

  \subsection{Molecule Parameterization}\label{method:molecule_parameterization}

@@
